### 2023-03-13 main/chapter_2ljets.tex
matrix method probabilities and uncertainties

To make FNP estimates in our regions, the Matrix Method is
implemented by assigning weights to observed data events that are then
histogrammed in the tighter selections of our search regions,
much like other samples~\cite{twoljets2018int}.
Systematic variations are assigned by comparing histograms when those weights
are varied according to various uncertainties in the Matrix Method procedure,
and statistical errors are assigned in the standard way from the samples
weights.

>>>>

The `real efficiency' transition probabilities, $\prob{t}{r,i}$, are estimated
from simulation by matching truth-level and reconstructed leptons; they
are assigned as functions of $|\eta|$ and $\pt$, and increase from
$\prob{t}{r,i} \approx 70\%$ at $\pt = 25\,\eV[G]$ to
$\prob{t}{r,i} \approx 95\%$ for $\pt > 100\,\eV[G]$ with small uncertainties.
The `fake rate' transition probabilities, $\prob{t}{f,i}$, are estimated
from the difference between simulation and data in selections that enhance the
fake lepton contribution; they are also assigned as functions of
$|\eta|$ and $\pt$, and are mostly small at around
$\prob{t}{f,i} \approx 10\%$.
Larger fake rates are seen for hard electrons with
$\pt > 100\,\eV[G]$, for which $\prob{t}{f,i} \approx 40\%$ due to
contributions from heavy-flavour decays.
Subtracting simulated backgrounds introduces an uncertainty of
around $\pm10\%$ on all fake rate estimates.

To make FNP estimates in our regions, the Matrix Method is
implemented by assigning weights to observed data events that are then
histogrammed in the tighter selections of our search regions,
much like other samples~\cite{twoljets2018int}.
Systematic variations are assigned by comparing histograms when those weights
are varied according to various uncertainties in the Matrix Method procedure,
and statistical errors are assigned in the standard way from the samples'
weights.
These systematic and statistical uncertainties are propagated separately,
and do impact our final results through their impact on the region-specific
fake estimates, which are described in
Section~\ref{sec:2ljets_matrix_method_ewk}.
